Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}

### 2019-04-14 manuscript.tex
work on final section; more figure and appendix edits

Researchers and consumers of conjoints can avoid the inferential errors that accompany conditional AMCEs by focusing attention on (subgroup) marginal means, differences between subgroup marginal means to infer subgroup differences in preferences toward particular features, and omnibus nested model comparisons to infer subgroup differences across many features. To demonstrate each of these three techniques

Here we provide a more complete example, demonstrating the full extent of this problem for interpretation of conjoint results and present alternative forms of analysis that more robustly convey subgroup preferences and the differences (if any) between them. Specifically, we show how reference category changes can lead to visual patterns of differences-in-AMCEs that provide strikingly different interpretations. We then show how to visualize and formally compare subgroup marginal means using simple means comparisons tests to avoid this problem. Finally, we demonstrate how to use nested model comparison tests to formally test for omnibus differences between groups.

Consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which show the exact same analysis (comparing AMCEs for high and low ethnocentrism respondents) on the same experimental data from \citeauthor{HainmuellerHopkinsYamamoto2014}'s immigration experiment. In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in preferences between the two subgroups. In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.\footnote{The appendix contains comparable plots for experiments by \citet{BechtelScheve2013} and \citet{TeeleKallaRosenbluth2018}.}

Panel A gives the impression that there are significant differences in preferences between high and low ethnocentrism respondents toward immigrants from different countries of origin, with different careers, and with different educational attainments. By contrast, Panel B gives the impression that these differences --- indeed all differences --- are negligible. The experimental data and analytic approach in the two portrayals is identical; the only difference is the choice of reference category for the profile features. Given what we have shown about the relationship between differences in conditional AMCEs and differences in conditional marginal means, Panel B is the more truthful visualization \citep{Cairo2016}. The differences between subgroup AMCEs there more accurately convey differences in underlying preferences because the reference categories used in Panel B are the most similar between the two groups. Yet even this may not \textit{perfectly} convey differences because no feature generates perfect agreement between the subgroups.

@@

Alternatively presenting subgroup differences using conditional marginal means (as in Figure \ref{fig:hainmueller_mm_diffs}) provides the intended descriptive comparison of subgroup preferences. Each dot and error bar represents the conditional marginal mean (and its standard error) for high ethnocentrism (in red) and low ethnocentrism (in blue) respondents. This display of conditional marginal means highlights just how similar the preferences are for the two groups. For example, in the first set of estimates, both groups of respondents display minimally positive preferences toward female immigrants and minimally negative preferences toward male immigrants, averaging across those immigrants' other profile features. The second set of estimates shows both group are also more favorable toward higher-educated immigrants and less favorable toward less-education immigrants with no visually apparent differences. The third set of estimates, related to language skills, shows again similar patterns: both groups are more favorable toward immigrants with higher English proficiency than immigrants with lower English proficiency.

These estimates are less obviously identical for the two groups but look quite close. To test for pairwise differences between high and low ethnocentrism respondents, we can calculate differences in conditional conditional marginal means at each feature level, with associated significance tests:

\begin{itemize}
\item spoke fluent English: 0.02 (0.02, $z_{\text{diff}}$=1.30, $p\leq 0.20$)
\item spoke broken English: 0.01 (0.02, $z_{\text{diff}}$=0.71, $p\leq 0.48$)
\item tried to speak English but was unable: -0.01 (0.02, $z_{\text{diff}}$=-0.78, $p\leq 0.43$)
\item spoke [language] and used an interpreter: -0.02 (0.02, $z_{\text{diff}}$=-1.22, $p\leq 0.22$)

\end{itemize}

\noindent These pairwise tests show that are our eyes have not deceived us. None of the level-specific differences in conditional marginal means are statistically distinguishable from zero. Were we interested in an omnibus tests of whether any of these differences were non-zero, we could perform a nested model comparison of two equations: (a) one estimating only marginal effects of the ``Language Skills'' feature levels, and (b) the same model with additional interactions between the subgrouping covariate and the feature levels. The test compares the sum of squared residuals for the two equations.

@@

As before, we can perform an omnibus tests for the presence of any subgroup differences across all features, again using nested model comparison of two equations: (a) one estimating only effects of the features, and (b) the same model with additional interactions between the subgrouping covariate and all features. The result of that test for differences by ethnocentrism from the immigration experiment is: F(98, 11402)=1.16, $p\leq0.14$, which further demonstrates that the substantive interpretation provided by \citet{HainmuellerHopkinsYamamoto2014} accurately identified a lack of between-group differences. By contrast, \citet{BechtelScheve2013} argue in their cross-country conjoint examining climate change agreements ``that individuals in all four countries largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}. Yet a nested model comparisons shows the countries do differ in their preferences F(54, 67982)=3.72, $p\leq0.00$. This cross-country variation is largely driven by differences in sensitivity to monthly household costs feature, F(15, 67995)=3.80, $p\leq0.00$, with the United Kingdom and United States being more cost sensitive than Germany and France as is plainly visible in a plot of marginal means by country (see SI).

This kind of nested model comparison test can also be used to assess heterogeneity across conjoint features \citep[see also][]{EgamiImai2018}. For example, \citet{TeeleKallaRosenbluth2018} report just such a test for how effects of features other than candidate sex may differ between male and female candidates, finding no such heterogeneity (8--9). Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to an quite different conclusion.

@@

\section{Hainmueller et al. (2014) Candidate Experiment}

\subsection{Replication using AMCEs}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sun Nov 25 10:42:42 2018
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lp{3in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Military Service & Did Not Serve & 0.00 &  &  \\ 
  Military Service & Served & 0.09 & 0.02 & 4.95 \\ 
  Religion & None & 0.00 &  &  \\ 
  Religion & Jewish & -0.04 & 0.03 & -1.42 \\ 
  Religion & Catholic & -0.02 & 0.03 & -0.56 \\ 
  Religion & Mainline protestant & -0.01 & 0.03 & -0.48 \\ 
  Religion & Evangelical protestant & -0.12 & 0.03 & -3.78 \\ 
  Religion & Mormon & -0.14 & 0.03 & -4.46 \\ 
  College & No BA & 0.00 &  &  \\ 
  College & Baptist college & 0.14 & 0.03 & 4.82 \\ 
  College & Community college & 0.15 & 0.03 & 5.17 \\ 
  College & State university & 0.19 & 0.03 & 6.77 \\ 
  College & Small college & 0.18 & 0.03 & 6.50 \\ 
  College & Ivy League university & 0.27 & 0.03 & 9.26 \\ 
  Profession & Business owner & 0.00 &  &  \\ 
  Profession & Lawyer & -0.02 & 0.03 & -0.71 \\ 
  Profession & Doctor & -0.02 & 0.03 & -0.53 \\ 
  Profession & High school teacher & -0.04 & 0.03 & -1.42 \\ 
  Profession & Farmer & -0.09 & 0.03 & -2.94 \\ 
  Profession & Car dealer & -0.23 & 0.03 & -7.24 \\ 
  Income & 32K & 0.00 &  &  \\ 
  Income & 54K & 0.02 & 0.03 & 0.82 \\ 
  Income & 65K & 0.06 & 0.03 & 2.26 \\ 
  Income & 92K & 0.03 & 0.03 & 1.12 \\ 
  Income & 210K & 0.07 & 0.03 & 2.41 \\ 
  Income & 5.1M & 0.01 & 0.03 & 0.25 \\ 
  Race/Ethnicity & White & 0.00 &  &  \\ 
  Race/Ethnicity & Native American & 0.02 & 0.03 & 0.85 \\ 
  Race/Ethnicity & Black & 0.03 & 0.03 & 1.22 \\ 
  Race/Ethnicity & Hispanic & -0.02 & 0.03 & -0.84 \\ 
  Race/Ethnicity & Caucasian & 0.00 & 0.03 & 0.18 \\ 
  Race/Ethnicity & Asian American & 0.04 & 0.03 & 1.51 \\ 
  Age & 36 & 0.00 &  &  \\ 
  Age & 45 & 0.03 & 0.03 & 0.88 \\ 
  Age & 52 & 0.02 & 0.03 & 0.78 \\ 
  Age & 60 & 0.00 & 0.03 & 0.14 \\ 
  Age & 68 & -0.06 & 0.03 & -2.17 \\ 
  Age & 75 & -0.15 & 0.03 & -5.06 \\ 
  Gender & Male & 0.00 &  &  \\ 
  Gender & Female & 0.00 & 0.02 & 0.09 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

@@

\subsection{Replication using MMs}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/hainmueller_candidate_mm_appendix-1}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Sun Nov 25 10:42:44 2018
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lp{3in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Military Service & Did Not Serve & 0.46 & 0.01 & -3.54 \\ 
  Military Service & Served & 0.54 & 0.01 & 3.55 \\ 
  Religion & None & 0.56 & 0.02 & 2.73 \\ 
  Religion & Jewish & 0.52 & 0.02 & 0.96 \\ 
  Religion & Catholic & 0.53 & 0.02 & 1.24 \\ 
  Religion & Mainline protestant & 0.54 & 0.02 & 2.06 \\ 
  Religion & Evangelical protestant & 0.44 & 0.02 & -3.05 \\ 
  Religion & Mormon & 0.42 & 0.02 & -4.04 \\ 
  College & No BA & 0.34 & 0.02 & -8.11 \\ 
  College & Baptist college & 0.48 & 0.02 & -0.83 \\ 
  College & Community college & 0.49 & 0.02 & -0.39 \\ 
  College & State university & 0.53 & 0.02 & 1.39 \\ 
  College & Small college & 0.52 & 0.02 & 0.99 \\ 
  College & Ivy League university & 0.62 & 0.02 & 6.27 \\ 
  Profession & Business owner & 0.57 & 0.02 & 3.35 \\ 
  Profession & Lawyer & 0.55 & 0.02 & 2.20 \\ 
  Profession & Doctor & 0.54 & 0.02 & 2.08 \\ 
  Profession & High school teacher & 0.53 & 0.02 & 1.44 \\ 
  Profession & Farmer & 0.48 & 0.02 & -0.98 \\ 
  Profession & Car dealer & 0.33 & 0.02 & -8.64 \\ 
  Income & 32K & 0.46 & 0.02 & -1.89 \\ 
  Income & 54K & 0.49 & 0.02 & -0.65 \\ 
  Income & 65K & 0.53 & 0.02 & 1.33 \\ 
  Income & 92K & 0.51 & 0.02 & 0.46 \\ 
  Income & 210K & 0.54 & 0.02 & 1.94 \\ 
  Income & 5.1M & 0.47 & 0.02 & -1.26 \\ 
  Race/Ethnicity & White & 0.48 & 0.02 & -0.88 \\ 
  Race/Ethnicity & Native American & 0.52 & 0.02 & 0.96 \\ 
  Race/Ethnicity & Black & 0.52 & 0.02 & 0.85 \\ 
  Race/Ethnicity & Hispanic & 0.47 & 0.02 & -1.59 \\ 
  Race/Ethnicity & Caucasian & 0.49 & 0.02 & -0.53 \\ 
  Race/Ethnicity & Asian American & 0.52 & 0.02 & 1.14 \\ 
  Age & 36 & 0.53 & 0.02 & 1.43 \\ 
  Age & 45 & 0.55 & 0.02 & 2.21 \\ 
  Age & 52 & 0.56 & 0.02 & 3.18 \\ 
  Age & 60 & 0.53 & 0.02 & 1.40 \\ 
  Age & 68 & 0.45 & 0.02 & -2.31 \\ 
  Age & 75 & 0.38 & 0.02 & -5.99 \\ 
  Gender & Male & 0.50 & 0.01 & -0.07 \\ 
  Gender & Female & 0.50 & 0.01 & 0.07 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

\section{Hainmueller et al. (2014) Immigration Experiment}

\subsection{Replication using AMCEs}

@@

@@

% latex table generated in R 3.5.2 by xtable 1.8-3 package
% Fri Mar 15 15:56:01 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lp{3in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Gender & female & 0.00 &  &  \\ 
  Gender & male & -0.03 & 0.01 & -3.25 \\ 
  Education & No formal education & 0.00 &  &  \\ 
  Education & Equivalent to completing fourth grade & 0.03 & 0.01 & 2.22 \\ 
  Education & Equivalent to completing eighth grade & 0.06 & 0.01 & 3.86 \\ 
  Education & Equivalent to completing high school & 0.12 & 0.01 & 7.98 \\ 
  Education & Equivalent to completing two years of college & 0.16 & 0.02 & 7.12 \\ 
  Education & Equivalent to completing a college degree & 0.19 & 0.02 & 8.26 \\ 
  Education & Equivalent to completing a graduate degree & 0.18 & 0.02 & 10.41 \\ 
  Language Skills & spoke fluent English & 0.00 &  &  \\ 
  Language Skills & spoke broken English & -0.06 & 0.01 & -4.98 \\ 
  Language Skills & tried to speak English but was unable & -0.13 & 0.01 & -11.11 \\ 
  Language Skills & spoke [language] and used an interpreter & -0.16 & 0.01 & -13.78 \\ 
  Country of Origin & India & 0.00 &  &  \\ 
  Country of Origin & Germany & 0.05 & 0.02 & 2.66 \\ 
  Country of Origin & France & 0.03 & 0.02 & 1.53 \\ 
  Country of Origin & Mexico & 0.01 & 0.02 & 0.59 \\ 
  Country of Origin & Philippines & 0.03 & 0.02 & 1.91 \\ 
  Country of Origin & Poland & 0.03 & 0.02 & 1.83 \\ 
  Country of Origin & China & -0.02 & 0.02 & -0.81 \\ 
  Country of Origin & Sudan & -0.04 & 0.02 & -2.01 \\ 
  Country of Origin & Somalia & -0.05 & 0.02 & -2.29 \\ 
  Country of Origin & Iraq & -0.11 & 0.02 & -5.56 \\ 
  Job & Janitor & 0.00 &  &  \\ 
  Job & Waiter & -0.01 & 0.02 & -0.41 \\ 
  Job & Child care provider & 0.01 & 0.02 & 0.89 \\ 
  Job & Gardener & 0.01 & 0.02 & 0.78 \\ 
  Job & Financial analyst & 0.06 & 0.03 & 2.17 \\ 
  Job & Construction worker & 0.04 & 0.02 & 2.26 \\ 
  Job & Teacher & 0.07 & 0.02 & 4.39 \\ 
  Job & Computer programmer & 0.08 & 0.03 & 2.76 \\ 
  Job & Nurse & 0.08 & 0.02 & 5.08 \\ 
  Job & Research scientist & 0.13 & 0.03 & 4.44 \\ 
  Job & Doctor & 0.16 & 0.03 & 5.49 \\ 
  Job Experience & No job training or prior experience & 0.00 &  &  \\ 
  Job Experience & One or two years of job training and experience & 0.07 & 0.01 & 5.92 \\ 
  Job Experience & Three to five years of job training and experience & 0.11 & 0.01 & 9.32 \\ 
  Job Experience & More than five years of job training and experience & 0.11 & 0.01 & 9.96 \\ 
  Job Plans & Has a contract with a U.S. employer & 0.00 &  &  \\ 
  Job Plans & Does not have a contract with a U.S. employer & -0.10 & 0.01 & -8.50 \\ 
  Job Plans & Will look for work after arriving in the U.S. & -0.12 & 0.01 & -10.69 \\ 
  Job Plans & Has no plans to look for work at this time & -0.28 & 0.01 & -23.91 \\ 
  Reason for Application & Reunite with family members already in the U.S. & 0.00 &  &  \\ 
  Reason for Application & Seek better job in U.S. & -0.04 & 0.01 & -4.37 \\ 
  Reason for Application & Escape political/religious persecution & 0.06 & 0.02 & 3.58 \\ 
  Prior Entry & Never been to the U.S. & 0.00 &  &  \\ 
  Prior Entry & Entered U.S. once before on a tourist visa & 0.06 & 0.01 & 4.49 \\ 
  Prior Entry & Has visited the U.S. many times before on tourist visas & 0.05 & 0.01 & 4.24 \\ 
  Prior Entry & Spent six months with family members in the U.S & 0.08 & 0.01 & 5.98 \\ 
  Prior Entry & Entered the U.S. once before without legal authorization & -0.11 & 0.01 & -8.45 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

@@

\subsection{Replication using MMs}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_mm_appendix-1}

>>>>

To begin, consider the left and right facets of Figure \ref{fig:hainmueller_subgroup_example_plot}, which shows estimated subgroup AMCEs for three features from the immigration study. In panel ``A'' (left), all features are configured so that the reference category is the one with the largest difference in levels of support between the two subgroups. In panel ``B'' (right), all features are configured so that the reference category is the one with the smallest difference in preferences between the two subgroups.

Panel A gives the impression that there are significant differences in preferences between high and low ethnocentrism respondents toward immigrants from different countries of origin, with different careers, and with different educational attainments because the reference category choice cascades the difference in reference category favorability into AMCEs for all other feature levels. By contrast, Panel B gives the impression that these differences are negligible. The experimental data and analytic approach in the two portrayals is identical; the only difference is the choice of reference category. Given what we have shown about the relationship between differences in conditional AMCEs and differences in conditional marginal means, Panel B is the more truthful visualization \citep{Cairo2016}. The differences between subgroup AMCEs there more accurately convey differences in underlying preferences because the reference categories used in Panel B are the most similar between the two groups.

@@

Next, making a comparison of levels of favorability toward different types of immigrants without using AMCEs would have been even more truthful. Figure \ref{fig:hainmueller_mm_diffs} \textit{directly} shows that comparison of preferences as differences in subgroup marginal means between the two groups for these three features, with 95\% confidence intervals for the difference.\footnote{A presentation of subgroup marginal means for all features can be found in Appendix \ref{app:hainmuellerimmigration}.} The two groups indeed have similar preferences, something that would have happened to be clear had the conditional AMCEs in the right panel of Figure \ref{fig:hainmueller_subgroup_example_plot} been presented but that would have been far less obvious were the conditional AMCEs in the left panel of that figure presented. Pairwise difference in means tests would provide formal procedures for testing the statistical significance of these differences.

Yet, finally, the similarity of subgroup preferences in conjoints is often characterized in an \textit{omnibus} fashion, as in the quote from \citet{HainmuellerHopkinsYamamoto2014} describing ``patterns of support.'' An appropriate test in such cases is one that evaluates whether a model of support that accounts for group differences better fits the data than a model of support with only conjoint features as predictors. This type of test is known as a ``nested model comparison'' which compares the fit of a ``restricted'' regression (the restriction being that interactions between features and a subgroup identifier are held to be zero) nested within an ``unrestricted'' regression that allows for arbitrary interactions between conjoint features and the subgroup identifier. Formally, a nested model comparison provides an F-test of the null hypothesis that all interaction terms are equal to zero.\footnote{Like any ANOVA this hypothesis test may yield substantively different insight from a series of tests of pairwise mean differences. Figure \ref{fig:hainmueller_mm_diffs} shows three instances where the confidence intervals for pairwise differences in marginal means do not include zero even though the omnibus test fails to reject the null.}

@@

As before, we can perform an omnibus tests for the presence of any subgroup differences across all features, again using nested model comparison of two equations: (a) one estimating only effects of the features, and (b) the same model with additional interactions between the subgrouping covariate and all features. The result of that test for differences by ethnocentrism from the immigration experiment is: F(98, 11402)=1.16, $p\leq0.14$, which further demonstrates that the substantive interpretation provided by \citet{HainmuellerHopkinsYamamoto2014} accurately identified a lack of between-group differences.

This kind of nested model comparison test can also be used to assess heterogeneity across conjoint features \citep[see also][]{EgamiImai2018}. For example, \citet{TeeleKallaRosenbluth2018} report just such a test for how effects of features other than candidate sex may differ between male and female candidates, finding no such heterogeneity (8--9). Fortunately, the original analysis accurately detected an absence of subgroup differences, yet a subtly different set of analytic decisions about reference categories (as shown in Figure \ref{fig:hainmueller_subgroup_example_plot}) could have led to a quite different conclusion. As an example, \citet{BechtelScheve2013} argue that their conjoint results show ``individuals in all four countries largely agree on which dimensions are important and to what extent'' \citep[13765]{BechtelScheve2013}, but a nested model comparison shows the countries do differ in their preferences F(54, 67982)=3.72, $p\leq0.00$. This cross-country variation largely driven by differences in sensitivity to monthly household costs feature, F(15, 67995)=3.80, $p\leq0.00$, with the United Kingdom and United States being more cost sensitive than Germany and France. Visual comparisons of conditional AMCEs can sometimes provide accurate insights into subgroup differences in preferences, but ulimately there is no guarantee that they do in any particular analysis.

@@

\section{Hainmueller et al. (2014) Candidate Experiment}\label{app:hainmuellercandidate}

\subsection{Replication using AMCEs and MMs}

@@

\subsection{Numerical Results: AMCEs}

% latex table generated in R 3.5.3 by xtable 1.8-3 package
% Sun Apr 14 20:35:25 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lp{3in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Military Service & Did Not Serve & 0.00 &  &  \\ 
  Military Service & Served & 0.09 & 0.02 & 4.95 \\ 
  Religion & None & 0.00 &  &  \\ 
  Religion & Jewish & -0.04 & 0.03 & -1.42 \\ 
  Religion & Catholic & -0.02 & 0.03 & -0.56 \\ 
  Religion & Mainline protestant & -0.01 & 0.03 & -0.48 \\ 
  Religion & Evangelical protestant & -0.12 & 0.03 & -3.78 \\ 
  Religion & Mormon & -0.14 & 0.03 & -4.46 \\ 
  College & No BA & 0.00 &  &  \\ 
  College & Baptist college & 0.14 & 0.03 & 4.82 \\ 
  College & Community college & 0.15 & 0.03 & 5.17 \\ 
  College & State university & 0.19 & 0.03 & 6.77 \\ 
  College & Small college & 0.18 & 0.03 & 6.50 \\ 
  College & Ivy League university & 0.27 & 0.03 & 9.26 \\ 
  Profession & Business owner & 0.00 &  &  \\ 
  Profession & Lawyer & -0.02 & 0.03 & -0.71 \\ 
  Profession & Doctor & -0.02 & 0.03 & -0.53 \\ 
  Profession & High school teacher & -0.04 & 0.03 & -1.42 \\ 
  Profession & Farmer & -0.09 & 0.03 & -2.94 \\ 
  Profession & Car dealer & -0.23 & 0.03 & -7.24 \\ 
  Income & 32K & 0.00 &  &  \\ 
  Income & 54K & 0.02 & 0.03 & 0.82 \\ 
  Income & 65K & 0.06 & 0.03 & 2.26 \\ 
  Income & 92K & 0.03 & 0.03 & 1.12 \\ 
  Income & 210K & 0.07 & 0.03 & 2.41 \\ 
  Income & 5.1M & 0.01 & 0.03 & 0.25 \\ 
  Race/Ethnicity & White & 0.00 &  &  \\ 
  Race/Ethnicity & Native American & 0.02 & 0.03 & 0.85 \\ 
  Race/Ethnicity & Black & 0.03 & 0.03 & 1.22 \\ 
  Race/Ethnicity & Hispanic & -0.02 & 0.03 & -0.84 \\ 
  Race/Ethnicity & Caucasian & 0.00 & 0.03 & 0.18 \\ 
  Race/Ethnicity & Asian American & 0.04 & 0.03 & 1.51 \\ 
  Age & 36 & 0.00 &  &  \\ 
  Age & 45 & 0.03 & 0.03 & 0.88 \\ 
  Age & 52 & 0.02 & 0.03 & 0.78 \\ 
  Age & 60 & 0.00 & 0.03 & 0.14 \\ 
  Age & 68 & -0.06 & 0.03 & -2.17 \\ 
  Age & 75 & -0.15 & 0.03 & -5.06 \\ 
  Gender & Male & 0.00 &  &  \\ 
  Gender & Female & 0.00 & 0.02 & 0.09 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

@@

\subsection{Numerical Results: MMs}

% latex table generated in R 3.5.3 by xtable 1.8-3 package
% Sun Apr 14 20:35:25 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lp{3in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Military Service & Did Not Serve & 0.46 & 0.01 & -3.54 \\ 
  Military Service & Served & 0.54 & 0.01 & 3.55 \\ 
  Religion & None & 0.56 & 0.02 & 2.73 \\ 
  Religion & Jewish & 0.52 & 0.02 & 0.96 \\ 
  Religion & Catholic & 0.53 & 0.02 & 1.24 \\ 
  Religion & Mainline protestant & 0.54 & 0.02 & 2.06 \\ 
  Religion & Evangelical protestant & 0.44 & 0.02 & -3.05 \\ 
  Religion & Mormon & 0.42 & 0.02 & -4.04 \\ 
  College & No BA & 0.34 & 0.02 & -8.11 \\ 
  College & Baptist college & 0.48 & 0.02 & -0.83 \\ 
  College & Community college & 0.49 & 0.02 & -0.39 \\ 
  College & State university & 0.53 & 0.02 & 1.39 \\ 
  College & Small college & 0.52 & 0.02 & 0.99 \\ 
  College & Ivy League university & 0.62 & 0.02 & 6.27 \\ 
  Profession & Business owner & 0.57 & 0.02 & 3.35 \\ 
  Profession & Lawyer & 0.55 & 0.02 & 2.20 \\ 
  Profession & Doctor & 0.54 & 0.02 & 2.08 \\ 
  Profession & High school teacher & 0.53 & 0.02 & 1.44 \\ 
  Profession & Farmer & 0.48 & 0.02 & -0.98 \\ 
  Profession & Car dealer & 0.33 & 0.02 & -8.64 \\ 
  Income & 32K & 0.46 & 0.02 & -1.89 \\ 
  Income & 54K & 0.49 & 0.02 & -0.65 \\ 
  Income & 65K & 0.53 & 0.02 & 1.33 \\ 
  Income & 92K & 0.51 & 0.02 & 0.46 \\ 
  Income & 210K & 0.54 & 0.02 & 1.94 \\ 
  Income & 5.1M & 0.47 & 0.02 & -1.26 \\ 
  Race/Ethnicity & White & 0.48 & 0.02 & -0.88 \\ 
  Race/Ethnicity & Native American & 0.52 & 0.02 & 0.96 \\ 
  Race/Ethnicity & Black & 0.52 & 0.02 & 0.85 \\ 
  Race/Ethnicity & Hispanic & 0.47 & 0.02 & -1.59 \\ 
  Race/Ethnicity & Caucasian & 0.49 & 0.02 & -0.53 \\ 
  Race/Ethnicity & Asian American & 0.52 & 0.02 & 1.14 \\ 
  Age & 36 & 0.53 & 0.02 & 1.43 \\ 
  Age & 45 & 0.55 & 0.02 & 2.21 \\ 
  Age & 52 & 0.56 & 0.02 & 3.18 \\ 
  Age & 60 & 0.53 & 0.02 & 1.40 \\ 
  Age & 68 & 0.45 & 0.02 & -2.31 \\ 
  Age & 75 & 0.38 & 0.02 & -5.99 \\ 
  Gender & Male & 0.50 & 0.01 & -0.07 \\ 
  Gender & Female & 0.50 & 0.01 & 0.07 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

@@

\section{Hainmueller et al. (2014) Immigration Experiment}\label{app:hainmuellerimmigration}

\subsection{Replication using AMCEs and MMs}

@@

\includegraphics[width=\maxwidth]{figure/hainmueller_immigration_amce_appendix-2}

@@

\subsection{Numerical Results: AMCEs}

% latex table generated in R 3.5.3 by xtable 1.8-3 package
% Sun Apr 14 20:35:34 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lp{3in}rrr}
  \hline
feature & level & estimate & std.error & z \\ 
  \hline
Gender & female & 0.00 &  &  \\ 
  Gender & male & -0.03 & 0.01 & -3.25 \\ 
  Education & No formal education & 0.00 &  &  \\ 
  Education & Equivalent to completing fourth grade & 0.03 & 0.01 & 2.22 \\ 
  Education & Equivalent to completing eighth grade & 0.06 & 0.01 & 3.86 \\ 
  Education & Equivalent to completing high school & 0.12 & 0.01 & 7.98 \\ 
  Education & Equivalent to completing two years of college & 0.16 & 0.02 & 7.12 \\ 
  Education & Equivalent to completing a college degree & 0.19 & 0.02 & 8.26 \\ 
  Education & Equivalent to completing a graduate degree & 0.18 & 0.02 & 10.41 \\ 
  Language Skills & spoke fluent English & 0.00 &  &  \\ 
  Language Skills & spoke broken English & -0.06 & 0.01 & -4.98 \\ 
  Language Skills & tried to speak English but was unable & -0.13 & 0.01 & -11.11 \\ 
  Language Skills & spoke [language] and used an interpreter & -0.16 & 0.01 & -13.78 \\ 
  Country of Origin & India & 0.00 &  &  \\ 
  Country of Origin & Germany & 0.05 & 0.02 & 2.66 \\ 
  Country of Origin & France & 0.03 & 0.02 & 1.53 \\ 
  Country of Origin & Mexico & 0.01 & 0.02 & 0.59 \\ 
  Country of Origin & Philippines & 0.03 & 0.02 & 1.91 \\ 
  Country of Origin & Poland & 0.03 & 0.02 & 1.83 \\ 
  Country of Origin & China & -0.02 & 0.02 & -0.81 \\ 
  Country of Origin & Sudan & -0.04 & 0.02 & -2.01 \\ 
  Country of Origin & Somalia & -0.05 & 0.02 & -2.29 \\ 
  Country of Origin & Iraq & -0.11 & 0.02 & -5.56 \\ 
  Job & Janitor & 0.00 &  &  \\ 
  Job & Waiter & -0.01 & 0.02 & -0.41 \\ 
  Job & Child care provider & 0.01 & 0.02 & 0.89 \\ 
  Job & Gardener & 0.01 & 0.02 & 0.78 \\ 
  Job & Financial analyst & 0.06 & 0.03 & 2.17 \\ 
  Job & Construction worker & 0.04 & 0.02 & 2.26 \\ 
  Job & Teacher & 0.07 & 0.02 & 4.39 \\ 
  Job & Computer programmer & 0.08 & 0.03 & 2.76 \\ 
  Job & Nurse & 0.08 & 0.02 & 5.08 \\ 
  Job & Research scientist & 0.13 & 0.03 & 4.44 \\ 
  Job & Doctor & 0.16 & 0.03 & 5.49 \\ 
  Job Experience & No job training or prior experience & 0.00 &  &  \\ 
  Job Experience & One or two years of job training and experience & 0.07 & 0.01 & 5.92 \\ 
  Job Experience & Three to five years of job training and experience & 0.11 & 0.01 & 9.32 \\ 
  Job Experience & More than five years of job training and experience & 0.11 & 0.01 & 9.96 \\ 
  Job Plans & Has a contract with a U.S. employer & 0.00 &  &  \\ 
  Job Plans & Does not have a contract with a U.S. employer & -0.10 & 0.01 & -8.50 \\ 
  Job Plans & Will look for work after arriving in the U.S. & -0.12 & 0.01 & -10.69 \\ 
  Job Plans & Has no plans to look for work at this time & -0.28 & 0.01 & -23.91 \\ 
  Reason for Application & Reunite with family members already in the U.S. & 0.00 &  &  \\ 
  Reason for Application & Seek better job in U.S. & -0.04 & 0.01 & -4.37 \\ 
  Reason for Application & Escape political/religious persecution & 0.06 & 0.02 & 3.58 \\ 
  Prior Entry & Never been to the U.S. & 0.00 &  &  \\ 
  Prior Entry & Entered U.S. once before on a tourist visa & 0.06 & 0.01 & 4.49 \\ 
  Prior Entry & Has visited the U.S. many times before on tourist visas & 0.05 & 0.01 & 4.24 \\ 
  Prior Entry & Spent six months with family members in the U.S & 0.08 & 0.01 & 5.98 \\ 
  Prior Entry & Entered the U.S. once before without legal authorization & -0.11 & 0.01 & -8.45 \\ 
   \hline
\end{tabular}
\endgroup
\end{table}

@@

\subsection{Numerical Results: MMs}
